Probabilistic Symbol Encoding for \\Convolutional Associative Memories

### 2017-01-20 papers/hrr-paper/paper.tex
Add experiment figure and text

>>>>

The symbolic scripting experiment is set up using a single-sensor Braitenberg
vehicle (see figures \ref{fig:experiment:agent1} and
\ref{fig:experiment:agent2}).
The sensor returns a list of objects in its field of view with their
corresponding view space positions in $[0,1]$ (far left to far right).
% note: it would be better if we probe with all returned objects and check the
% result, but IIRC this did not work well. maybe figure it out?
All returned objects are then compared to the agent's target object.
If the target is found, the holographic controller is probed with its view space
position which, due to the similarity of scalar values, yields results even for
values that lie between the originally stored values and can consequently be
probed with the symbols $left\_wheel$ and $right\_wheel$ to extract the symbolic
actions $forwards$ or $backwards$.
If the target is not found or no action could be determined, the agent defaults
to probing the controller with the symbolic constant $no\_object$ which results
a clockwise rotation when probing for wheel actions (see figure
\ref{fig:experiment:similar2}).

In the left column of figure \ref{fig:experiment}, the agent approaches the blue
target (figure \ref{fig:experiment:agent1}). In the beginning (tick $-50$), the
agent rotates right (default action) because the target is not visible.
At tick $-30$, the object enters the agent's visual field and is consequently
centered until tick $-19$.
Then, with the sensory value of ${\sim}0.5$, the actions for both wheels switch
to $forwards$ (figure \ref{fig:experiment:similar1}) and the agent approaches
the target, constantly decreasing its distance
(figure \ref{fig:experiment:distance1}).

In the right column of figure \ref{fig:experiment}, the target is not currently
in the visual field of the agent.
This is due to reaching its old target at approximately tick $-13$ which leads
to the removal of all current objects and random placement of new objects,
including one target.
As the new object is placed outside of the agent's field of view, the default
action of probing $no\_object$ is performed constantly.
As described, this then results in the encoded default actions $backwards$ for
probing with $left\_wheel$ and $forwards$ for probing with $right\_wheel$---a
clockwise rotation (see figure \ref{fig:experiment:similar2}).

This experiment shows the effectiveness of our approach in a practical
application by encoding symbolic sensing, actuators and actions in a symbolic
controller.

\begin{figure}%[th!]
\center
\begin{subfigure}{.47\columnwidth}
	\center
	{%
	\setlength{\fboxsep}{0pt}%
	%\setlength{\fboxrule}{1pt}%
	\fbox{\includegraphics[width=.98\columnwidth]{img/exp_robot_139.png}}%
	}%
	\caption{Scene of Agent 1 with three randomly placed items, the blue
	one being the target object.
	The green fan represents the visual field.}
	\label{fig:experiment:agent1}
\end{subfigure}
\begin{subfigure}{.47\columnwidth}
	\center
	{%
	\setlength{\fboxsep}{0pt}%
	%\setlength{\fboxrule}{1pt}%
	\fbox{\includegraphics[width=.98\columnwidth]{img/robot_235.png}}%
	}%
	\caption{Scene of Agent 2 with three randomly placed items.
	The agent does not have the target object in his field of view (green
	fan).}
	\label{fig:experiment:agent2}
\end{subfigure}
\begin{subfigure}{.49\columnwidth}
	\center
	\includegraphics[width=.98\columnwidth]{img/3_139.pdf}
	\caption{Symbolic sensing with target in visual field results in scalar
	value representing target direction (${\sim}0.55$, almost straight
	forward).}
	\label{fig:experiment:sensor1}
\end{subfigure}
\begin{subfigure}{.49\columnwidth}
	\center
	\includegraphics[width=.98\columnwidth]{img/3_235.pdf}
	\caption{Symbolic sensing without target in visual field showing the
	representation for the symbolic constant $no\_object$.}
	\label{fig:experiment:sensor2}
\end{subfigure}
\begin{subfigure}{.49\columnwidth}
	\center
	\includegraphics[width=.98\columnwidth]{img/1_139.pdf}
	\caption{Target position over time in the visual field of Agent 1.
	At tick $-30$, it appears on the far right edge and then gradually
	shifts towards the center.}
	\label{fig:experiment:pos1}
\end{subfigure}
\begin{subfigure}{.49\columnwidth}
	\center
	\includegraphics[width=.98\columnwidth]{img/1_235.pdf}
	\caption{Agent 2 lost track of the target object (red background).
	In this case, the old target was reached and the new target is not in
	the field of view yet.}
	\label{fig:experiment:pos2}
\end{subfigure}
\begin{subfigure}{.49\columnwidth}
	\center
	\includegraphics[width=.98\columnwidth]{img/4_139.pdf}
	\caption{Distance between Agent 1 and its target over time.
	Here, the blue object in \subref{fig:experiment:agent1} is being
	approached.}
	\label{fig:experiment:distance1}
\end{subfigure}
\begin{subfigure}{.49\columnwidth}
	\center
	\includegraphics[width=.98\columnwidth]{img/4_235.pdf}
	\caption{Distance between Agent 2 and its target over time.
	At tick $-12$ a new target was added (black bar).}
	\label{fig:experiment:distance2}
\end{subfigure}
\begin{subfigure}{.49\columnwidth}
	\center
	\includegraphics[width=.98\columnwidth]{img/2_139.pdf}
	\caption{Similarities of $left\_wheel$ and $right\_wheel$ to
	the $forwards$ and $backwards$ actions respectively.
	Here, Agent 1 approaches its target because $forwards$ has the
	highest similarity for both wheels.}
	\label{fig:experiment:similar1}
\end{subfigure}
\begin{subfigure}{.49\columnwidth}
	\center
	\includegraphics[width=.98\columnwidth]{img/2_235.pdf}
	\caption{Similarities as described in \subref{fig:experiment:similar1}
	for Agent 2. As no target is in the visual field, the default action for
	the symbol $no\_object$ is performed (rotate right).}
	\label{fig:experiment:similar2}
\end{subfigure}
\caption{Excerpts from our symbolic scripting experiment, controlling a
Braitenberg vehicle with one linear sensor.
The left column (\protect\subref{fig:experiment:agent1},
\protect\subref{fig:experiment:sensor1}, \protect\subref{fig:experiment:pos1},
\protect\subref{fig:experiment:distance1} and
\protect\subref{fig:experiment:similar1}) illustrates an agent approaching a
target in its visual field.
The right column (\protect\subref{fig:experiment:agent2},
\protect\subref{fig:experiment:sensor2}, \protect\subref{fig:experiment:pos2},
\protect\subref{fig:experiment:distance2},
\protect\subref{fig:experiment:similar2}) shows an agent without a target in its
visual field, rotating clockwise (\protect\subref{fig:experiment:similar2}) to
find it.
}
\label{fig:experiment}
